Verifying Demonstrations

### 2017-08-11 conclusions.tex

In general, none of the related works fulfils the authenticity requirements 
(\cref{%
  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated%
}).
Some of the schemes provide some limited verifiability, i.e.\ mostly universal 
verifiability (\cref{UniversalVerif}), but not individual verifiability 
(\cref{IndividualVerif}) nor eligibility verifiability 
(\cref{EligibilityVerif}).

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack authenticity and verifiability.
      \item Some provide universal verifiability (V\ref{UniversalVerif}).
    \end{itemize}
  \end{remark}
\end{frame}

>>>>

In general, none of the related works fulfils the eligibility verifiability 
\cref{%
  CountOnce,%
  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated,%
}.
To some extent, some techniques do fulfil \cref{DesignatedEvent}, since people 
usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
not individual verifiability (\cref{IndividualVerif}).
If they would provide individual verifiability, they would likely violate the 
privacy requirements.
And finally, most of the current methods are estimates, with quite some error 
margins, so they cannot give the correct participation count.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack most of verifiability.
      \item Some provide universal verifiability (V\ref{UniversalVerif}).

        \pause

      \item Most cannot estimate the correct participation count.
    \end{itemize}
  \end{remark}
\end{frame}

### 2017-08-11 intro.tex
Moves properties into introduction

After many demonstrations the count by police and that by the organizers 
differ, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
establishing the actual number of participants.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
We will discuss them in more detail in \cref{RelatedWork}.

@@

%However, to complicate things further,
%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
%  getting text messages, phone calls and being required to attend political 
%  rallies during work hours
%}.
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Venezuela is banning protests that could "disturb or affect" Sunday's 
%  controversial election for a new constituent assembly.
%}
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Prison terms of between five and 10 years could be imposed on those 
%  contravening the ban,
%}
%
%\blockcquote{VenezuelanGovtBansProtesting}{%
%  Venezuelans are planning to defy a government ban on public demonstrations 
%  and risk deadly repression with marches across the country to protest against 
%  a vote Sunday that opposition forces say will mark the end of democracy
%}

>>>>

After many demonstrations the count by police and that by the organizers 
differ\footnote{%
  This is actually quite natural, they have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
}, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
establishing the actual number of participants.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
We will discuss them in more detail in \cref{RelatedWork}.

@@

% Verifiability and privacy
\mode<all>
\input{properties.tex}
